Decision Support and Health Insurance Choice

### 2021-03-18 finals/Paper.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Decision Support and Health Insurance Choice},
  pdfauthor={Ian McCarthy \& Evan Saltzman},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{setspace}
\doublespacing
\usepackage{titlesec}
\titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Decision Support and Health Insurance Choice}
\author{Ian McCarthy \& Evan Saltzman}
\date{September 02, 2020}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan. Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market (Abaluck and Gruber 2011; Ketcham et al. 2012; Gruber 2017). One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA). In this paper, we examine the role of this decision assistance on health insurance plan choice and its implications for consumer welfare.

\hypertarget{background-and-motivation}{%
\section{Background and Motivation}\label{background-and-motivation}}

@@

\hypertarget{data}{%
\section{Data}\label{data}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{discrete-choice-framework}{%
\subsection{Discrete Choice Framework}\label{discrete-choice-framework}}

We model health insurance purchasing with a nested logit discrete choice model, as in Saltzman (2019), and we derive estimates of the effect of decision assistnce by embedding this discrete choice model into a standard potential outcomes framework.

@@

\hypertarget{dominated-choices}{%
\subsection{Dominated Choices}\label{dominated-choices}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-abaluck2011}{}%
Abaluck, Jason, and Jonathan Gruber. 2011. ``Heterogeneity in Choice Inconsistencies Among the Elderly: Evidence from Prescription Drug Plan Choice.'' \emph{American Economic Review} 101 (3): 377--81.

\leavevmode\hypertarget{ref-gruber2017}{}%
Gruber, Jonathan. 2017. ``Delivering Public Health Insurance Through Private Plan Choice in the United States.'' \emph{Journal of Economic Perspectives} 31 (4): 3--22.

\leavevmode\hypertarget{ref-ketcham2012}{}%
Ketcham, Jonathan D, Claudio Lucarelli, Eugenio J Miravete, and M Christopher Roebuck. 2012. ``Sinking, Swimming, or Learning to Swim in Medicare Part d.'' \emph{American Economic Review} 102 (6): 2639--73.

\leavevmode\hypertarget{ref-saltzman2019}{}%
Saltzman, Evan. 2019. ``Demand for Health Insurance: Evidence from the California and Washington Aca Exchanges.'' \emph{Journal of Health Economics} 63: 197--222.
\end{cslreferences}

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx,amssymb,amsmath,setspace,comment,verbatim,titling,pgf,lscape,color}
\usepackage[left=2cm,right=2cm,top=2.5cm,bottom=2cm]{geometry}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{array}
\usepackage{bbm}
\usepackage{marginnote}
\usepackage[justification=centering]{caption}
%%\usepackage{breqn}
\newcommand{\pderiv}[2]{\frac{\partial#1}{\partial#2}}
%\usepackage{siunitx}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
\hypersetup{colorlinks,%
						citecolor=black,%
						filecolor=black,%
						linkcolor=black,%
						urlcolor=blue,%
						}
\setstretch{1.5}

\setlength{\droptitle}{-50pt}

\begin{document}
\title{Decision Support and Health Insurance Choice}
\author{Ian McCarthy \& Evan Saltzman}
\date{March 18, 2021}
\maketitle

\vspace{-2ex}
\begin{abstract}
\noindent Abstract
\end{abstract}

\clearpage

\section{Introduction}
\label{sec:introduction}

Health insurance markets are unique in many respects, not least of which is the increasing complexity of choosing an optimal health insurance plan. Such complexity has been well-documented in studies of health insurance choice in the Medicare Advantage market \citep{abaluck2011, ketcham2012, gruber2017}. One way to reduce the burden of this complexity is to provide professional decision support through private insurance agents or public assistance programs, both of which are available in the California health insurance exchanges created under the Affordable Care Act (ACA). In this paper, we examine the role of this decision assistance on health insurance plan choice and its implications for consumer welfare.

\section{Background and Motivation}
\label{sec:background-and-motivation}

@@

\section{Data}
\label{sec:data}

@@

\section{Methods}
\label{sec:methods}

@@

\subsection{Discrete Choice Framework}
\label{subsec:discrete-choice-framework}

We model health insurance purchasing with a nested logit discrete choice model, as in \cite{saltzman2019}, and we derive estimates of the effect of decision assistance by embedding this discrete choice model into a standard potential outcomes framework.

@@

\subsection{Dominated Choices}
\label{subsec:dominated-choices}

@@

\section{Results}
\label{sec:results}

@@

\section{Conclusion}
\label{sec:conclusion}

@@

\pagebreak
\bibliographystyle{authordate1}
\bibliography{BibTeX_Library}

\clearpage
\newpage

\section*{Tables and Figures}

\begin{figure}[htb]\caption{Count of Enrollees in California Exchange}
\centering
 		\hspace*{-1cm}\includegraphics[scale=.7]{figures/enrollee_count.png}
 		\begin{minipage}{\textwidth}
		\bigskip
			\footnotesize \textsc{Notes:} The coefficients for high ratings are shown with circles, those for middle ratings are shown with triangles, and no reviews are shown with diamonds. The main results are designated in blue along with an indicator for specification ``Main". Various specifications and required minimum number of reviews are also indicated. 
 		\end{minipage}
 		\label{figure:SpecCurve}
 \end{figure}
